\TESS Photometric Mapping of a Terrestrial Planet in the Habitable Zone: Detection of Clouds, Oceans, and Continents

### 2019-03-25 tex/ms.tex
map labels
more text

\todo{(figure showing lightcurves for various targets)}

@@

@@

@@

@@

\acknowledgements{\todo{(Artist acknowledgement)} The authors gratefully 
acknowledge Dan Foreman-Mackey, David W Hogg, Ben Pope, \todo{and ...} 
for useful conversations. Crucial parts of this work were carried out at the 
TESS Data Workshop, hosted by Space Telescope Science Institute, and the 
Building Early Science with TESS Workshop, hosted by the University of Chicago.}
\facility{TESS}
\software{Astropy, Matplotlib, Numpy, \starry \citep{Luger2019}, TensorFlow}
% Bibliography
\pagebreak
\bibliography{bib}

>>>>

Figure showing lightcurves for various targets: Figure~\ref{fig:data}.

@@

\subsection{Orbital Modeling}

We downloaded 
\footnote{\url{https://archive.stsci.edu/missions/tess/models/}}
the Solar System and \tess ephemeris data for
Sectors 1 and 2 and used \spiceypy \citep{Acton1996, Acton2017, Annex2017}
to convert the TDB timestamps to 
ephemeris time (ET). We then used the \textsf{spkezr} utility to compute
the relative positions of Sol, Sol d, and \tess for every cadence
in our dataset in the J2000 equatorial reference frame. In this right-handed
coordinate frame, Sol d is centered at the origin, the $y$ axis points along the 
planet's spin axis, and the $x$ axis points toward the vernal equinox. We
do not apply any light travel correction, as the expected delay is on the order
of a few seconds.

At any given cadence, we rotate Sol d about its spin axis to the correct phase,
assuming a rotational period of $1.00$ day. We determine the initial rotation
phase of Sol d by computing the Sol d Rotation Angle (ERA), given by \citep{Urban2013}
%
\begin{align}
\mathrm{ERA} = 360^\circ(0.7790572732640 + 1.00273781191135448 \, t_U) \, \mathrm{mod} \, 360^\circ
\end{align}
%
where $t_U = t - 2451545.0$. At $t = t_0 = 2458325.5$, the first timestamp in our dataset,
we find $\mathrm{ERA} = 303.4^\circ$, meaning the vernal equinox will be aligned with
the prime meridian $360^\circ - 303.4^\circ = 56.6^\circ = 3.77$ hours past $t_0$.
%
Finally, we rotate the frame to align
\tess with the $+z$ axis, with the spin vector of Sol d along the $y-z$ plane.

@@

\begin{figure}[t!]
    \begin{centering}
    \includegraphics[width=\linewidth]{figures/map_labels.pdf}
    \caption{\label{fig:map_labels}
             Labeled map of Sol d.
             \codelink{earthshine_S1_S2}
             }
    \end{centering}
\end{figure}

@@

No zonal cloud bands: prior.

@@

\acknowledgements{\todo{(Artist acknowledgement)} The authors gratefully 
acknowledge Dan Foreman-Mackey, David W Hogg, Ben Pope, \todo{and ...} 
for useful conversations. Crucial parts of this work were carried out at the 
TESS Data Workshop, hosted by Space Telescope Science Institute, and the 
Building Early Science with TESS Workshop, hosted by the University of Chicago.}
\facility{TESS}
\software{Astropy, Matplotlib, Numpy, \starry \citep{Luger2019}, TensorFlow, \spiceypy \citep{Annex2019}}
% Bibliography
\pagebreak
\bibliography{bib}
